Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-06-21 paper/paper.tex
minor cosmetics in the cvnn section

This $\cplx \simeq \real^2$ identification allows straightforward retrofitting of $\cplx$VNN
into existing $\real$-valued auto-differentiation frameworks for deep learning. This
act is backed by Wirtinger ($\cplx\real$) calculus, which enables generalized treatment
of functions of complex argument, by regarding $z$ and $\conj{z}$ as independent variables
and defining derivatives with respect to them through partial derivatives with respect
to real and imaginary parts of each argument. These definitions simplify manual calculations
of $\cplx$ derivatives and satisfy the product and chain rules, respect complex conjugation
and linearity for $\cplx \to \cplx$ maps. $\cplx\real$ calculus was used to define $\cplx$
version of back-propagation, \citep{benvenuto_complex_1992,guberman_complex_2016}. However,
since auto-differentiation frameworks can algorithmically handle computational graphs
of arbitrary complexity, explicit use of Wirtinger derivatives is not required, especially
considering the fact that the direction of the steepest ascent of a $\cplx\to \real$
function is given by complex conjugate gradient $\nabla_{\conj{z}}$, which coincides
with the classical gradient of the same function viewed as $\real^2 \to \real$,
(see appendix~\ref{sub:wirtinger_calculus}).
%
% in natively $\cplx$-valued backprop it would be necessary to modify the existing sgd
% to explicitly use $\nabla_{\conj{z}} f(z)$, while no such modification is necessary
% in re-im. If some inner activation of a $\cplx$VNN is holomorphic, i.e. satisfies
% Cauchy-Riemann conditions, then that particular step of in the chain rule that is
% backprop can be simplified by assuming one piece of the tracked gradient to be exact
% zero. But other wise it is necessary to track both $\partial_{\conj{z}}$ and $\partial_{z}$.
%
% Training a $\cplx$VNN involves optimizing a real-valued objective with respect to
% complex valued arguments.
%
% The computed gradients are theoretically justified
% - CR dictates the it is necessary to track both $z$ and $\conj{z}$ derivatives
% - the direction of largest increase in f: C-R is given by the gradient with
% respect to the conjugate, which coincides in the re-im representation with 
% the ordinary gradient wrt u and v
% - the Chain Rule in CR holds and when a holomorphic C-C function is backproped
% the autodiff just wastes cycles on computing its conj-derivative (rather than assuming
% it to be zero)

>>>>

This $\cplx \simeq \real^2$ identification allows straightforward retrofitting of $\cplx$VNN
into existing $\real$-valued auto-differentiation frameworks for deep learning. This
act is backed by Wirtinger ($\cplx\real$) calculus, which enables generalized treatment
of functions of complex argument, by regarding $z$ and its \emph{complex conjugate}
$\conj{z}$ as independent variables and defining derivatives with respect to them through
partial derivatives with respect to real and imaginary parts. These definitions simplify
manual calculations of $\cplx$ derivatives and satisfy the product and chain rules, respect
complex conjugation and linearity for $\cplx \to \cplx$ maps. $\cplx\real$ calculus was
used to define $\cplx$ version of back-propagation,
\citep{benvenuto_complex_1992,guberman_complex_2016}.
However, since auto-differentiation frameworks can algorithmically handle computational
graphs of arbitrary complexity, explicit use of Wirtinger derivatives is not required,
especially considering the fact that the direction of the steepest ascent of a $
  \cplx \to \real
$ function is given by complex conjugate gradient $\nabla_{\conj{z}}$, which coincides
with the classical gradient of the same function viewed as $\real^2 \to \real$,
(see appendix~\ref{sub:wirtinger_calculus}).
%
% in natively $\cplx$-valued backprop it would be necessary to modify the existing sgd
% to explicitly use $\nabla_{\conj{z}} f(z)$, while no such modification is necessary
% in re-im. If some inner activation of a $\cplx$VNN is holomorphic, i.e. satisfies
% Cauchy-Riemann conditions, then that particular step of in the chain rule that is
% backprop can be simplified by assuming one piece of the tracked gradient to be exact
% zero. But other wise it is necessary to track both $\partial_{\conj{z}}$ and $\partial_{z}$.
%
% Training a $\cplx$VNN involves optimizing a real-valued objective with respect to
% complex valued arguments.
%
% The computed gradients are theoretically justified
% - CR dictates the it is necessary to track both $z$ and $\conj{z}$ derivatives
% - the direction of largest increase in f: C-R is given by the gradient with
% respect to the conjugate, which coincides in the re-im representation with 
% the ordinary gradient wrt u and v
% - the Chain Rule in CR holds and when a holomorphic C-C function is backproped
% the autodiff just wastes cycles on computing its conj-derivative (rather than assuming
% it to be zero)
